### 2023-01-08 output/DiD/tables/balance_table.tex
balance table v1

\begin{tabular}{llcccccc}
\toprule
 &  & \textit{Cases Won by Plaintiff} & \textit{('Difference in Cases Won by Defendant', 'Unweighted')} & \textit{('Difference in Cases Won by Defendant', 'P-Value')} \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.33 \\
 & For cause (transfer) & 0.00 & -0.01 & 0.02 \\
 & Foreclosure & 0.04 & 0.03 & 0.00 \\
 & Foreclosure (transfer) & 0.00 & -0.00 & 0.77 \\
 & No cause & 0.11 & -0.02 & 0.08 \\
 & No cause (transfer) & 0.01 & -0.01 & 0.08 \\
 & Non-payment of rent & 0.71 & 0.01 & 0.78 \\
 & Non-payment of rent (transfer) & 0.01 & -0.01 & 0.02 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 \\
 & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.37 \\
 & Plaintiff is an entity & 0.66 & 0.03 & 0.13 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6554743.50 & 184134.63 & 0.79 \\
 & Building value & 1897711.00 & 25986.91 & 0.90 \\
 & Land value & 87585.64 & 22095.39 & 0.21 \\
 & Other value & 8535625.58 & 232361.89 & 0.78 \\
 & Units & 28.73 & -24.04 & 0.00 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccccc}
\toprule
 &  & \textit{} & \multicolumn{2}{r}{\textit{Difference in Cases Won by Defendant}} \\
 &  & Cases Won by Plaintiff & Unweighted & P-Value \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.33 \\
 & For cause (transfer) & 0.00 & -0.01 & 0.02 \\
 & Foreclosure & 0.04 & 0.03 & 0.00 \\
 & Foreclosure (transfer) & 0.00 & -0.00 & 0.77 \\
 & No cause & 0.11 & -0.02 & 0.08 \\
 & No cause (transfer) & 0.01 & -0.01 & 0.08 \\
 & Non-payment of rent & 0.71 & 0.01 & 0.78 \\
 & Non-payment of rent (transfer) & 0.01 & -0.01 & 0.02 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 \\
 & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.37 \\
 & Plaintiff is an entity & 0.66 & 0.03 & 0.13 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Total property value & 6554743.50 & 184134.63 & 0.79 \\
 & Building value & 1897711.00 & 25986.91 & 0.90 \\
 & Land value & 87585.64 & 22095.39 & 0.21 \\
 & Other value & 8535625.58 & 232361.89 & 0.78 \\
 & Units & 28.73 & -24.04 & 0.00 \\
\cline{1-5}
\bottomrule
\end{tabular}
